Turbulence in compact to giant HII regions

### 2022-02-18 strucfunc_paper.tex
Fix example strucfunc figure and references to observed figures

Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. The solid circles indicate the range use in the non-linear regression analysis (see section~\ref{sec:methods-apply}), while the open circles are the points of the structure function that where left out.
This was done to enhance the possibilities of a convergence since the structure function values at large separations are to follow the 2\(\sigma^2\) value according to theory.
The light shaded areas in the plots show where the separation \(r\) is above half of the box size \(L\), which is indicated with a vertical dotted line.

@@

Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
They also show the marginalized distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.

The results shown on left panels on Figures \ref{fig:strucfunc-fit-A}-\ref{fig:strucfunc-fit-D} show a typical second-order structure function pattern, where there is a series of ascending values of  the structure function that tends to stabilize around the 2\(\sigma^2\) value, indicating a loss in the correlations at large separations. 
The Carina nebula and Hubble X follow this behavior.

@@

The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex, finding no indication of turbulent motions between scale of 10 and 100 pc.
These result is consistent with Fig. \ref{fig:strucfunc-fit-B}a showing that the turbulent motions are correlated at scales \(<\) \SI{5}{pc}.
\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula as their observations cover a region where the large-scale velocity fluctuations are uncorrelated as in the case of \citet{1961MNRAS.122....1F}.
From the observations where are using this is the first time turbulence characterized in 30 Doradus using the structure function.

For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
Despite this general agreement the interpretations in each study is different.
\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{00}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.  
\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall in this range would make the structure function flat and scales \(<\)\SI{10}{pc}.
Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution, so they rule out \citet{Medina-Tanco:1997a} results. 
Our Fig. \ref{fig:strucfunc-fit-C}e shows in fact that there is a velocity structure in NGC 604. 
We have prove that a consistent and more precise method in analyzing structure function is key to obtaining trustworthy results.
None of the previous studies present a power-law index for the structure function to compare our results.

>>>>

Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. The solid circles indicate the range use in the non-linear regression analysis (see section~\ref{sec:methods-apply}), while the open circles are the points of the structure function that where left out.
This was done to enhance the possibilities of a convergence since the structure function values at large separations are to follow the 2\(\sigma^2\) value according to theory.
The light shaded areas in the plots show where the separation \(r\) is above half of the box size \(L\), which is indicated with a vertical dotted line.

@@

Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
They also show the marginalized distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.

The results shown on left panels on Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} show a typical second-order structure function pattern, where there is a series of ascending values of  the structure function that tends to stabilize around the 2\(\sigma^2\) value, indicating a loss in the correlations at large separations. 
The Carina nebula and Hubble X follow this behavior.

@@

The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex, finding no indication of turbulent motions between scale of 10 and 100 pc.
These result is consistent with Fig. \ref{fig:strucfunc-fit-Dor} showing that the turbulent motions are correlated at scales \(<\) \SI{5}{pc}.
\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula as their observations cover a region where the large-scale velocity fluctuations are uncorrelated as in the case of \citet{1961MNRAS.122....1F}.
From the observations where are using this is the first time turbulence characterized in 30 Doradus using the structure function.

For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
Despite this general agreement the interpretations in each study is different.
\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{00}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.  
\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall in this range would make the structure function flat and scales \(<\)\SI{10}{pc}.
Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution, so they rule out \citet{Medina-Tanco:1997a} results. 
Our Fig. \ref{fig:strucfunc-fit-N604H} shows in fact that there is a velocity structure in NGC 604. 
We have prove that a consistent and more precise method in analyzing structure function is key to obtaining trustworthy results.
None of the previous studies present a power-law index for the structure function to compare our results.
